A Large-Scale Study of the Use of Eval in R

### 2020-08-21 inst/paper/main.tex
The four eval functions

\lstset{ 
	language=R,                     % the language of the code
	basicstyle=\tiny\ttfamily, % the size of the fonts that are used for the code
	numbers=left,                   % where to put the line-numbers
	numberstyle=\tiny\color{Blue},  % the style that is used for the line-numbers
	stepnumber=1,                   % the step between two line-numbers. If it is 1, each line
	% will be numbered
	numbersep=5pt,                  % how far the line-numbers are from the code
	backgroundcolor=\color{white},  % choose the background color. You must add \usepackage{color}
	showspaces=false,               % show spaces adding particular underscores
	showstringspaces=false,         % underline spaces within strings
	showtabs=false,                 % show tabs within strings adding particular underscores
	%frame=single,                   % adds a frame around the code
	rulecolor=\color{black},        % if not set, the frame-color may be changed on line-breaks within not-black text (e.g. commens (green here))
	tabsize=2,                      % sets default tabsize to 2 spaces
	captionpos=b,                   % sets the caption-position to bottom
	breaklines=true,                % sets automatic line breaking
	breakatwhitespace=false,        % sets if automatic breaks should only happen at whitespace
	keywordstyle=\color{RoyalBlue},      % keyword style
	commentstyle=\color{YellowGreen},   % comment style
	stringstyle=\color{ForestGreen}      % string literal style
} 
\begin{document}

@@

\renewcommand{\c}[1]{{\texttt{#1}}\xspace}
\newcommand{\miss}[1]{{\textcolor{red}{#1}}\xspace}

@@

There are four different kinds of \c{eval} in the \emph{base} package:  \c{eval}, \c{evalq}, \c{eval.parent},  \c{local}.
The most important one is \c{eval}: \lstinline|eval(expr, envir, enclos)|

- the four eval functions in base

>>>>

\lstset{ 
	language=R,                     % the language of the code
	basicstyle=\ttfamily, % the size of the fonts that are used for the code
	numbers=left,                   % where to put the line-numbers
	numberstyle=\color{Blue},  % the style that is used for the line-numbers
	stepnumber=1,                   % the step between two line-numbers. If it is 1, each line
	% will be numbered
	numbersep=2pt,                  % how far the line-numbers are from the code
	backgroundcolor=\color{white},  % choose the background color. You must add \usepackage{color}
	showspaces=false,               % show spaces adding particular underscores
	showstringspaces=false,         % underline spaces within strings
	showtabs=false,                 % show tabs within strings adding particular underscores
	%frame=single,                   % adds a frame around the code
	rulecolor=\color{black},        % if not set, the frame-color may be changed on line-breaks within not-black text (e.g. commens (green here))
	tabsize=2,                      % sets default tabsize to 2 spaces
	captionpos=b,                   % sets the caption-position to bottom
	breaklines=true,                % sets automatic line breaking
	breakatwhitespace=false,        % sets if automatic breaks should only happen at whitespace
	keywordstyle=\color{RoyalBlue},      % keyword style
	commentstyle=\color{YellowGreen},   % comment style
	stringstyle=\color{ForestGreen}      % string literal style
} 
\begin{document}

@@

\renewcommand{\c}[1]{\lstinline{#1}\xspace}
\newcommand{\miss}[1]{{\textcolor{red}{#1}}\xspace}
\newcommand{\eval}{\c{eval}}

@@

There are four different kinds of \eval in the \emph{base} package:  \c{eval}, \c{evalq}, \c{eval.parent},  \c{local}.
The most important one is \eval:

\begin{lstlisting}
eval <- function (expr, envir = parent.frame(), enclos = if (is.list(envir) || 
is.pairlist(envir)) parent.frame() else baseenv()) 
.Internal(eval(expr, envir, enclos))
\end{lstlisting}

The three other functions are defined using \lstinline|eval|.

\begin{lstlisting}
evalq <- function (expr, envir = parent.frame(), enclos = if (is.list(envir) || 	is.pairlist(envir)) parent.frame() else baseenv()) 
	.Internal(eval(substitute(expr), envir, enclos))

eval.parent <- function (expr, n = 1) 
{
p <- parent.frame(n + 1)
eval(expr, p)
}

local <- function (expr, envir = new.env()) eval.parent(substitute(eval(quote(expr), envir)))
\end{lstlisting}
